An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2015-01-07 mixedwindow.tex
Several minor edits and corrections

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative models with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternatives that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic to have mean-zero under the null.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.} %
However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is a
random walk \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

This paper proposes a modified version of their statistic and shows that it is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently argued,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new
statistic.  Section~\ref{sec:2} presents simulations that compare our
pairwise \oos\ test to \poscw\ original statistics.
Section~\ref{sec:3} demonstrates the use of our statistic by
reanalyzing \citepos{GoW:08} study of excess return predictability and
demonstrates how our results can be used in settings with many
alternative models. Section~\ref{sec:4} concludes. Proofs of our
results have been put in a separate Appendix along with some
supporting results \citep{Cal:15}.

@@

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In their 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
rolling window as the $\yh_{t+1}$. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

@@

Last, we define some notation that will be used to derive the
theoretical properties of our \oos\ statistics.  The information set
that contains the information available for forecasting $y_{t+1}$ is
\begin{equation*}
  \Fs_t = \sigma(y_t, x_{t+1}, z_{t+1}, y_{t-1}, x_t, z_t,\dots).
\end{equation*}
The adjusted \oos\ loss for the alternative model using a hypothetical
value of $\beta$ to produce the benchmark forecast is denoted by
\begin{equation*}
  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
\end{equation*}
Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
\begin{gather*}
  \gh_t = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{s+1}) x_s'\Bigg]\,
          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
  \intertext{and}
  g_t = \E\Big[(4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
\end{gather*}
and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
$\fb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.

@@

Note that these results allow misspecification; asymptotic normality
follows from the weak dependence of the underlying series and from the
design of the test statistic. These statistics have typically been
used to test the null hypothesis that the benchmark model is correctly
specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
implies that $f_t(\btrue) - \E f_t(\btrue)$ is an \mds\ as discussed
at the beginning of the Section. This is especially appealing in our
framework, since the benchmark can be theoretically motivated so the
\mds\ null would be a test of rationality. For example, \citet{GoW:08}
test whether excess returns for the S\&P 500 are predictable
out-of-sample, and any deviation from an \mds\ is potentially
interesting. But the \mds\ null hypothesis only affects the estimator
of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.

In other settings, a researcher may want to test the weaker hypothesis
that $\E \fb^* = 0$ but the benchmark may be misspecified. This
approach can then be interpreted as an encompassing test as in
\citet{HLN:98}, and would test whether the alternative model contains
additional information that would make the benchmark model more
accurate. This interpretation comes from the combination forecasting
model
\begin{equation*}
  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\beta + w \yh_{t+1}
\end{equation*}
which can be rewritten in terms of forecast errors as
\[
e_{\mathit{avg},t+1} = e_{0,t+1} + w (e_{0,t+1} - e_{1,t+1})
\]
with $e_{\mathit{avg},t+1} = y_{t+1} - \yh_{\mathit{avg},t+1}$,
$e_{0,t+1} = y_{t+1} - x_t'\beta$, and $e_{1,t+1} = y_{t+1} -
\yh_{1,t+1}$. The value
\[
w = \frac{\E e_{0,t+1} (e_{0,t+1} - e_{1,t+1})}{\E e_{0,t+1}^2}
\]
minimizes the \mse\ of the combination forecast, so the combination
model will have smaller \mse\ than the benchmark model unless
$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated, implying that
the alternative uses information not in the benchmark.  As the
discussion at the beginning of this section shows, the test in
Theorem~\ref{res:1} is equivalent to a test of zero correlation
between $e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$.

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
  \mathit{predictor}_{t} + \ep_{t+1},
\end{equation*}
where $\beta_{0}$ and
$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the \emph{predictor} column of
Table~\ref{tab:em1}. \citep[See][for a detailed description of the
variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance.
There are several approaches that could accommodate this multiplicity, and a full
treatment is beyond the scope of this paper, however, it is
straightforward to use Theorem~\ref{res:1} and Lemma~\ref{lem:2} to
derive an appropriate critical value similar to~\citet{Whi:00}.

@@

To estimate $V$, we use the correlation matrix associated with the
multivariate analogue of $\sigmah_2$,
\[
\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
\]
where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
\begin{gather*}
  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
  \intertext{and}
  \gh_{it} = \Bigg[\oavg{s} (4 x_s'\bh_s - 2 y_{s+1} - 2 \yh_{i,s+1}) x_s'\Bigg]\,
            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
\end{gather*}
respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
$1 - \alpha$ quantile of the distribution of $\max_i \hat W_i$, with
$\hat W \sim N(0, \hat V)$.  Then
\begin{equation*}
  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{1i} > \hat c\Big] \leq \alpha,
\end{equation*}
under the null hypothesis that excess returns are an \mds\ with
respect to all of the information contained in the variables listed in
Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
value.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here.} %

We calculate $\hat c$ by generating \empiricaldraws\ draws from
$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
remain significant at 10\% using this critical value. Using this
critical value, none of the predictors are significant at 10\%, which
gives additional support to \citepos{GoW:08} conclusion that excess
returns are unpredictable and also demonstrates the importance of
correcting for multiplicity in these studies.

>>>>

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative model with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternatives that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic to have mean-zero under the null.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  assume that the models do not converge to the same limit,
  which rules out nesting.} %
However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is
not estimated \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

This paper proposes a modified version of Clark and West's (2006,
2007) statistic and shows that it is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently argued,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new
statistic.  Section~\ref{sec:2} presents simulations that compare our
pairwise \oos\ test to \poscw\ original statistics.
Section~\ref{sec:3} demonstrates the use of our statistic by
reanalyzing \citepos{GoW:08} study of excess return predictability and
demonstrates how our results can be used in settings with many
alternative models. Section~\ref{sec:4} concludes. Our results follow
from arguments similar to \citepos{Wes:96} and have been put in a
separate appendix along with some supporting lemmas \citep{Cal:15}.

@@

\citet{ClW:06,ClW:07} propose using this as a test of whether $\ep_{t+1}$ is
an \mds. In their 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
their 2007 paper, where $\btrue$ is unknown and estimated with the same length-$R$
rolling window as the $\yh_{t+1}$. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimator of $\btrue$ does not converge to $\btrue$.

@@

Last, we define some notation that will be used to derive the
theoretical properties of our \oos\ statistics.  The information set
that contains the information available for forecasting $y_{t+1}$ is
\begin{equation*}
  \Fs_t = \sigma(y_t, x_t, z_t, y_{t-1}, x_{t-1}, z_{t-1},\dots).
\end{equation*}
The adjusted \oos\ loss for the alternative model using a hypothetical
value of $\beta$ to produce the benchmark forecast is denoted by
\begin{equation*}
  f_t(\beta) = (y_{t+1} - x_t'\beta)^2 - (y_{t+1} - \yh_{t+1})^2 + (x_t'\beta - \yh_{t+1})^2.
\end{equation*}
Define the additional terms $\fh_t = f_t(\bh_t)$, $f_t = f_t(\btrue)$,
\begin{gather*}
  \gh_t = 2 \Bigg[\oavg{s} (x_s'\bh_s - \yh_{s+1}) x_s'\Bigg]\,
          \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
  \intertext{and}
  g_t = 2 \E\Big[(x_t'\btrue - \yh_{t+1}) x_t'\Big] \, (\E x_t x_t')^{-1} x_t \ep_{t+1}
\end{gather*}
and the \oos\ averages $\fb = \osum{t} \fh_t/P$, $\fb^* = \osum{t} f_t/P$,
$\gb = \osum{t} \gh_t/P$, and $\gb^* = \osum{t} g_t/P$.

@@

Note that these results allow misspecification; asymptotic normality
follows from the weak dependence of the underlying series and from the
design of the test statistic. These statistics have typically been
used to test the null hypothesis that the benchmark model is correctly
specified --- that $\{\ep_t, \Fs_t\}$ is an \mds\ --- which
implies that $f_t(\btrue) - \E f_t(\btrue)$ is an \mds\ as discussed
at the beginning of this section. This is especially appealing in our
framework, since the benchmark can be theoretically motivated so the
\mds\ null would be a test of rationality. For example, \citet{GoW:08}
test whether excess returns for the S\&P 500 are predictable
out-of-sample, and any deviation from an \mds\ is potentially
interesting. But the \mds\ null hypothesis only affects the estimator
of $\sigma^2$ (see Lemma~\ref{lem:2}); Theorem~\ref{res:1} continues
to hold under any \dgp\ that satisfies Assumptions~\ref{a1}~--~\ref{a4}.

In other settings, a researcher may want to test the weaker hypothesis
that $\E \fb^* = 0$ but the benchmark may be misspecified. This
approach can then be interpreted as an encompassing test as in
\citet{HLN:98}, and would test whether the alternative model contains
additional information that would make the benchmark model more
accurate. This interpretation comes from the combination forecasting
model
\begin{equation*}
  \yh_{\mathit{avg},t+1} = (1 - w) x_t'\beta + w \yh_{t+1}
\end{equation*}
which can be rewritten in terms of forecast errors as
\[
e_{\mathit{avg},t+1} = e_{0,t+1} + w (e_{0,t+1} - e_{1,t+1})
\]
with $e_{\mathit{avg},t+1} = y_{t+1} - \yh_{\mathit{avg},t+1}$,
$e_{0,t+1} = y_{t+1} - x_t'\beta$, and $e_{1,t+1} = y_{t+1} -
\yh_{1,t+1}$. The value
\[
w = \frac{\E e_{0,t+1} (e_{0,t+1} - e_{1,t+1})}{\E e_{0,t+1}^2}
\]
minimizes the \mse\ of the combination forecast, so the combination
model will have smaller \mse\ than the benchmark model, implying that
the alternative uses information not in the benchmark, unless
$e_{0,t+1}$ and $e_{0,t+1} - e_{1,t+1}$ are uncorrelated.

@@

Here, we conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
  \mathit{predictor}_{t} + \ep_{t+1},
\end{equation*}
where $\beta_{0}$ and
$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the \emph{predictor} column of
Table~\ref{tab:em1}. \citep[See][for a detailed description of the
variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

@@

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance.
There are several approaches that could accommodate this multiplicity and a full
treatment is beyond the scope of this paper, however, it is
straightforward to use our results to
derive a valid critical value similar to~\citet{Whi:00}.

@@

To estimate $V$, we use the correlation matrix associated with the
multivariate analogue of $\sigmah_2$,
\[
\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
\]
where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
\begin{gather*}
  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
  \intertext{and}
  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
\end{gather*}
respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
$\hat W \sim N(0, \hat V)$.  Then
\begin{equation*}
  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
\end{equation*}
under the null hypothesis that excess returns are an \mds\ with
respect to all of the information contained in the variables listed in
Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
value.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here.} %

We calculate $\hat c$ by generating \empiricaldraws\ draws from
$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
remain significant at 10\% with this critical value. Using this
critical value, none of the predictors are significant, which
gives additional support to \citepos{GoW:08} conclusion that excess
returns are unpredictable and also demonstrates the importance of
correcting for multiplicity in these studies.
